The impact of gas bulk rotation on the Lyman $\alpha$ line

### 2014-05-26 paper/ms.tex
typos in conclusions

Our main result is two-fold. First,rotation clearly impacts the \ly line
morphology. Second, rotation introduces an anisotropy for different
viewing angles. For viewing angles close to the poles the line is
double peaked and it makes a transition to a single peaked line for
high rotational velocities and viewing angles along the equator. This
trend is stronger for spheres with homogeneusly distributed radiation
sources.  In contrast, the total flux in the line remains independent
of the viewing angle.

The escape fraction remains constant for diffenret viewing angles only
in the case of centrally distributed sources. In contrast, for an homogeneous
distribution the escape fraction decreases with high rotation 
fraction remain constant for different viewing angles. We showed that
these results can be interpreted in terms of the average number of
scatterings for the photons, a quantity that also remains constant
independent of the viewing angle and the rotational velocity for
centrally distributed sources and decreases for homogenously
distributed source.

@@

\item Rotation induces a considerable asymmetry in the morphology 
 of the spectra when the viewing angle $\theta$. This occurs for
 all of our models. The asymmetry is such that observeds with
 $\cos\theta\equiv \mu\sim 1$, i.e. observes aligned with the rotation
 axis, the line is double peaked while for $\mu\sim 0$ and high
 rotation veolcities the linebecomes double peaked.

>>>>

Our main result is two-fold. First,rotation clearly impacts the \ly line
morphology. Second, rotation introduces an anisotropy for different
viewing angles. For viewing angles close to the poles the line is
double peaked and it makes a transition to a single peaked line for
high rotational velocities and viewing angles along the equator. This
trend is stronger for spheres with homogeneously distributed radiation
sources.  In contrast, the total flux in the line remains independent
of the viewing angle.

The escape fraction remains constant for different viewing angles only
in the case of centrally distributed sources. In contrast, for an homogeneous
distribution the escape fraction decreases with high rotation 
fraction remain constant for different viewing angles. We showed that
these results can be interpreted in terms of the average number of
scatterings for the photons, a quantity that also remains constant
independent of the viewing angle and the rotational velocity for
centrally distributed sources and decreases for homogeneously
distributed source.

@@

\item Rotation induces a considerable asymmetry in the morphology 
 of the spectra when the viewing angle $\theta$. This occurs for
 all of our models. The asymmetry is such that observers with
 $\cos\theta\equiv \mu\sim 1$, i.e. observes aligned with the rotation
 axis, the line is double peaked while for $\mu\sim 0$ and high
 rotation velocities the line becomes double peaked.
